msc dissertation

### 2021-08-20 index.Rmd
latest

Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file. But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv, not read.csv.

>>>>

Because the orginal data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file. But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv, not read.csv.
